---
title: "Vungle"
author: "Roopa,  Uros"
date: "October 12, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. What is Vungle's data problem? What do they want to achieve? (1 Point)
- They use 1/16 of the data to test the algorythm and they are trying to see which algorithm is the better one. The problem that arises is that the sample may be bised since it's such a small portion of the whole data set. Ideally they should have set that to be random as well. 

2. Provide a brief description of the variables in the dataset. (1 Points)
- We are provided the variales 
3. What are the key variables for the manager? Are they present in the data? If not, how
would you create them? (1 Point)

4. Provide summary statistics for key variables via appropriate plots or tables. Do they
differ by Ad Campaign? (2 Points)

5. How would you test for ad effectiveness from this data? What is the null and alternate
hypotheses for your test(s)? (2 Points)

6. Conduct the hypothesis test(s) and interpret the results (2 Points)

7. What is your final recommendation to the manager at Vungle? (1 Point)


#Load the data and split it into two data frames for comparison 
```{r}
install.packages('dplyr')
library(dplyr)

install.packages('xlsx')
library(xlsx)
data <- read.xlsx("C:/Users/Uros Randelovic/Documents/R workspace/BUS 111/Vungle/vungle data.xlsx",2
          )
View(data)

Data1 <- subset(data, Strategy %in% c("Vungle A"))
Data2 <- subset(data, Strategy =="Vungle B")
View(Data1)
View(Data2)
#drop uncessary columns
Data1 <- subset(Data1, select = c(1:7))
Data2 <- subset(Data2, select = c(1:7))
#since the absoulte numbers are different calculate rations provided in the case
#to compare the models 
#TODO: charts exploring the data

#creating a dataframe to store the calculations
compareData <- data.frame(fillRate=double(),
                 completeRate=double(),
                 clickRate=double(),
                 conversionRate=double(),
                 stringsAsFactors=FALSE)

View(compareData)
#equalize the number of rows
compareData <- cbind(Data1,compareData)
#delete all columns
compareData <- subset(compareData, select = -c(1:28))
#dataset 1
Data1$completeRate <- Data1$Completes/Data1$Impressions
Data1$clickRate <- Data1$Clicks/Data1$Impressions
Data1$conversionRate <- Data1$Installs/Data1$Impressions
#load to compare data frame
compareData <- cbind(Data1$completeRate,compareData)
compareData <- cbind(Data1$clickRate,compareData)
compareData <- cbind(Data1$conversionRate,compareData)
summary(compareData)
```


```{r}
#dataset 2
Data2$completeRate <- Data2$Completes/Data1$Impressions
Data2$clickRate <- Data2$Clicks/Data1$Impressions
Data2$conversionRate <- Data2$Installs/Data1$Impressions
#load to compare data frame
compareData <- cbind(Data2$completeRate,compareData)
compareData <- cbind(Data2$clickRate,compareData)
compareData <- cbind(Data2$conversionRate,compareData)
#TODO: add a summary table
summary(compareData)
```


```{r}
#differences in ratios 
compareData$clickDiff <- compareData$`Data2$clickRate`- compareData$`Data1$clickRate`
compareData$completeDiff <- compareData$`Data2$completeRate`- compareData$`Data1$completeRate`
compareData$converseionDiff <- compareData$`Data2$conversionRate`- compareData$`Data1$conversionRate`
#summary table of these three variables - means that algorithm b did a porer job than the algorythm A

#calculate erpm difference
compareData$erpmDiff <- Data2$eRPM- Data1$eRPM
#look at the side by side comparison of A and B algorythm and their effectiveness
summary(select(.data = compareData, clickDiff, completeDiff,converseionDiff,erpmDiff))
```



```{r}

```

